Staged Compilation With Two-Level Type Theory

### 2022-02-14 paper/paper.tex
stuff

>>>>

Stability means that staging an object-level construction does nothing. However,
it turns out that the induction motive for contexts is necessarily the existence
of generic semantic contexts. We define a $\blank^P$ family of functions by
induction on object syntax. The induction motives are as follows.
\begin{alignat*}{4}
  & (\Gamma : \Cono)^P                    &&: |\ev\,\emb{\Gamma}|\,\Gamma\\
  & (\sigma : \Subo\,\Gamma\,\Delta)^P    &&: \Delta^P[\sigma] = |\ev\,\emb{\sigma}|\,\Gamma^P\\
  & (A      : \Ty_{\mbbo j}\,\Gamma)^P      &&: A = |\ev\,\emb{A}|\,\Gamma^P\\
  & (t      : \Tm_{\mbbo j}\,\Gamma\,A)^P   &&: t = |\ev\,\emb{t}|\,\Gamma^P
\end{alignat*}
The $\blank^P$ interpretation of all structure is straightforward. In
particular, we do not have to show preservation of any definitional equality,
since types, terms and substitutions are all interpreted as proof-irrelevant
equations.

TODO example

\begin{definition} We define \textbf{open staging} as follows.
\begin{alignat*}{4}
  & \Stage : \Ty_{0,j}\,\emb{\Gamma} \to \Ty_{\mbbo j}\,\Gamma \hspace{2em} && \Stage : \Tm_{0,j}\,\emb{\Gamma}\,A \to \Tm_{\mbbo j}\,\Gamma\,(\Stage\,A) \\
  & \Stage\,A := |\ev\,A|\,\Gamma^P && \Stage\,t := |\ev\,t|\,\Gamma^P
\end{alignat*}
\end{definition}

\begin{theorem} Open staging is stable.
\end{theorem}
\begin{proof} For $A : \Ty_{\mbbo j}$, $\Stage\,\emb{A}$ is by definition $|\ev\,\emb{A}|\,\Gamma^P$,
  hence by $A^P$ it is equal to $A$. Likewise, $\Stage\,\emb{t}$ is equal to $t$ by $t^P$.
\end{proof}

%% Δᴾ[σ] = |F⌜σ⌝| Γᴾ
%% (A : TyB Γ)ᴾ    : A = |F⌜A⌝| Γᴾ
%% (t : TmB Γ A)ᴾ  : t = |F⌜t⌝| Γᴾ
